### 2019-10-22 README.Rmd
one more update to talking points
updated to do list
added to questions for tomorrow

- What names should I give to the diagnostic plots?
- Color themes for the paper?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

@@

- draft methods section of the paper
- draft data example section of paper
- draft discussion section of paper
- draft appendices

>>>>

- Can we talk about the LIME assumptions?
- What names should I give to the diagnostic plots?
- Could you help me with the interpretation of the default LIME explanations?
- Metrics:
    - MSEE (mean squared explanation error?) versus locality metric which would need to be computed via the perturbations
    - Do we want to think of a metric that is stand alone? - not just for comparisons

**Graphics Group**

- Treats?

**Sandia**

@@

- draft paper
- start organizing literature review paper
